\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
tweak

In addition, we assume that many entries in the $D$-vector will be zero
(the ``sparsity'' assumption).
In order to encourage this, we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + \lambda\,||P\cdot\theta||_1^1\right]
\label{eq:objective}\quad ,
\end{eqnarray}
where
$\lambda$ is a regularization parameter,
$P$ is a projection operator that selects out from the $\theta$ vector only those components
that pertain to the \apogee\ spectral pixels,
and $||y||_1^1$ is the L1-norm or sum of absolute values of the components of $y$.
This kind of regularization adds a convex term to the optimization and leads to
sparse optima.
The $P$ operator makes it such that we only regularize the components of $\theta$ that multiply
the spectral pixels; we ask for the spectral model to be sparse but we don't ask for the photometric
model to be sparse.
We set the value of $\lambda$ by a 
very coarse cross-validation.

@@

From the \apogee\ data on these low-$\logg$ stars, we take the spectral pixels,
of which there are 7405 (after cutting out pixels that rarely or never get data),
on a common rest-frame wavelength grid.
That is, every \apogee\ star is extracted on (or interpolated to)
the same wavelength scale.
In detail, we obtain the
the \apogee\ spectral pixels from the pipeline-generated \code{aspcapStar} files.
We then pseudo-continuum-normalize the spectra according to the procedure developed
in \project{The~Cannon} (HOGG CITE):
That is, the pseudo-continuum is a spline fit to a set
of pixels chosen to be insensitive to stellar parameters.
We use as our spectral data the normalized spectral pixel values.

>>>>

In addition, we assume that many entries in the parameter $D$-vector $\theta$ will be zero
(the ``sparsity'' assumption).
In order to encourage this, we optimize not $\chi^2$ but a regularized objective function
\begin{eqnarray}
\hat{\theta} &\leftarrow& \argmin_{\theta}\left[\frac{1}{2}\,\chi^2(\theta) + \lambda\,||P\cdot\theta||_1^1\right]
\label{eq:objective}\quad ,
\end{eqnarray}
where
$\lambda$ is a regularization parameter,
$P$ is a projection operator that selects out from the $\theta$ vector only those components
that pertain to the \apogee\ spectral pixels,
and $||y||_1^1$ is the L1-norm or sum of absolute values of the components of $y$.
This kind of regularization adds a convex term to the optimization and leads to
sparse optima.
The $P$ operator makes it such that we only regularize the components of $\theta$ that multiply
the spectral pixels; we ask for the spectral model to be sparse but we don't ask for the photometric
model to be sparse.
We set the value of $\lambda$ by a 
very coarse cross-validation.

@@

From the \apogee\ data on these low-gravity stars, we take the spectral pixels,
of which there are 7405 (after cutting out pixels that rarely or never get data),
on a common rest-frame wavelength grid.
That is, every \apogee\ star is extracted on (or interpolated to)
the same wavelength scale.
In detail, we obtain the
the \apogee\ spectral pixels from the pipeline-generated \code{aspcapStar} files.
We then pseudo-continuum-normalize the spectra according to the procedure developed
in \project{The~Cannon} (HOGG CITE):
That is, the pseudo-continuum is a spline fit to a set
of pixels chosen to be insensitive to stellar parameters.
We use as our spectral data the normalized spectral pixel values.
